PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-01-31 txt/manuscript.tex
Update manuscript

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this 
column} \\
\hline
C1 & Current code version & 0.1.0 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/iitis/PyQBench} \\
\hline
C3 & Code Ocean compute capsule & \todo[inline]{???}\\
\hline
C4 & Legal Code License & Apache License 2.0\\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, Qiskit, AWS Braket \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & 
\texttt{Python >= 3.8}\newline
\texttt{amazon-braket-sdk \textapprox= 1.33.0}\newline
\texttt{numpy \textapprox= 1.14.5}\newline
\texttt{scipy \textapprox= 1.7.3}\newline
\texttt{pandas \textapprox= 1.5.0}\newline
\texttt{pydantic \textapprox= 1.9.0}\newline
\texttt{qiskit \textapprox= 0.39.0}\newline
\texttt{mthree \textapprox= 1.1.0}\newline
\texttt{tqdm \textapprox= 4.64.1}\newline
\texttt{pyyaml \textapprox= 6.0} \todo[inline]{everything???}\\
\hline 
C8 & If available Link to developer documentation/manual & \todo[inline]{???}\\
\hline
C9 & Support email for questions & \url{dexter2206@gmail.com}\\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

@@

>>>>

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this
column} \\
\hline
C1 & Current code version & 0.1.0 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/iitis/PyQBench} \\
\hline
C3 & Code Ocean compute capsule & \todo[inline]{???}\\
\hline
C4 & Legal Code License & Apache License 2.0\\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, Qiskit, AWS Braket \\
\hline
C7 & Compilation requirements, operating environments \& dependencies &
\texttt{Python >= 3.8}\newline
\texttt{numpy \textapprox= 1.22.0}\newline
\texttt{scipy \textapprox= 1.7.0}\newline
\texttt{pandas \textapprox= 1.5.0}\newline
\texttt{amazon-braket-sdk >= 1.11.1}\newline
\texttt{pydantic \textapprox= 1.9.1}\newline
\texttt{qiskit \textapprox= 0.37.2}\newline
\texttt{mthree \textapprox= 1.1.0}\newline
\texttt{tqdm \textapprox= 4.64.1}\newline
\texttt{pyyaml \textapprox= 6.0}\newline
\texttt{qiskit-braket-provider \textapprox= 0.0.3}\\
\hline
C8 & If available Link to developer documentation/manual &
\url{https://pyqbench.readthedocs.io/en/latest/}\\
\hline
C9 & Support email for questions & \url{dexter2206@gmail.com}\\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{}
\end{table}

@@

Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market,
with a wide selection of devices based on different architectures and accompanying software
solutions. Among hardware providers offering public access to their gate--based devices, one could
mention Rigetti, IBM, Oxford Quantum Group, IonQ or Xanadu. Other vendors offer devices operating in
different paradigms. Notably, one could mention D-Wave and their quantum
annealers, or QuEra devices based on neural atoms. \todo[inline]{Expand this list and provide short
description of those architectures}. Most vendors provide their own software stack and
application programming interface for accessing their devices. To name a few, Rigetti's computers
are available through their Forest SDK and PyQuil library and IBM Q computers can be accessed
through Qiskit or IBM Quantum Experience web interface. Some cloud services, like Amazon Braket, offer access to several quantum devices under a unified API. On top of that, several
libraries and frameworks can integrate with different hardware vendors. Examples of such frameworks
include IBM Q's Qiskit or Zapata Computing's Orquestra.

It is well known that NISQ devices have their limitations. The question is to what extent those
devices can perform meaningful computations? To answer this question, one has to devise a
methodology for benchmarking them. For gate--based computers, on which this paper focuses, there
already exist several approaches. \todo[inline]{List the methods}.

\todo[inline]{What benchmarking techniques are readily available?}

In this paper, we introduce yet another method for benchmarking gate--based devices with a simple
operational interpretation. In our method, we test how well the given device can distinguish between
two von Neumann measurements performed in different bases. We implemented our method in an
open-source Python library called PyQBench. The library supports any device available through Qiskit
library, and thus can be used with providers such as IBM Q or Amazon Braket. Along with the library,
the PyQBench package contains a command line tool for running benchmarks in most common scenarios.

\begin{itemize}
	\item NISQs are becoming widespread and easily available for the general audience
	\item As with any computational technology, there's a need for benchmarking NISQs to assess
	their potential usability.
	\item Our work aims to provide a new benchmarking scheme for gate-based devices.
	\item Why is PyQBench important?
	\begin{itemize}
		\item There exist multiple benchmarking methods already on the market
		\item Most of them have the following drawbacks:
		\begin{itemize}
			\item Their interpretation is not very intuitive (We cannot phrase it like this without
			explaining why it is so)
			\item Hard to use (is this true?)
			\item No libraries are readily available in Python (needs to be checked).
		\end{itemize}
		\item PyQBench is easy to install, it works with any Qiskit backend, and its results are
		easy to understand and interpret.
	\end{itemize}
\end{itemize}
